HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-16 paper/main.tex
sss

%composite score (uniform, sub-sets, weighted rather not -- according to categories [or empirically according to agreement])

\subsection{Annotation Interface.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Annotation Interface.}

We turn to discuss the interface for collecting human judgements on the semantic units of the source,
relating to the translation. UCCA annotations of the source are done offline, using the UCCA web
application\footnote{See UCCA webpage.}.

\figref{fig:interface} presents the user interface of HUME. The sentence at the top
shows the complete MT system output. The source sentence appears at the top, and
the source translation directly below it. Underneath the source sentence appears
its list of semantic units. For each semantic unit, including the one for the
entire source sentence, there is a textbox, displaying the yield of that unit.
Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the left of the unit's box.

The interface presents, for each unit, the segment of the translation which aligns to it.
This allows the user, especially in long sentences, to focus her attention on the parts
mostly likely to be relevant for her judgement. As the alignments are automatically derived,
and therefore noisy, the annotator is instructed to treat the aligned text is a cue, but to ignore
it and make a judgement according to the full translation sentence, in cases where the alignment
is misleading.

Concretely, let $s = (w_1,\ldots,w_n)$ be a source sentence, $t = (w'_1,\ldots,w'_n)$ a translation,
and $A \subset 2^{s \times t}$ a many-to-many word alignment between them.
If $u$ is a semantic unit in $s$, whose yield is $yld(u)$, we define the aligned text in
$t$ to be $a(u)=\bigcup_{(x_s,x_t) \in A \wedge x_s \cap yld(u) \neq \emptyset} x_t$.
As $a(u)$ may not be contiguous in the text, we mark all intervening units in red.

The child components of a structural node are marked with different coloured rectangles.
When navigating through the different
source sentence nodes, one can see the relevant sections of the translation because the aligned words in the translation are
highlighted in the complete sentence above. Aligned translations are also shown in black alongside the source node. If the node
is aligned to a set of discontiguous words in the translation, then the unaligned words that appear in between the aligned words
are shown in red. Even if these words are not directly aligned to the source node, they will likely change the meaning of the
translation and must be considered when marking the translation as correct or not. The alignments are just meant as a guide. The
annotator should look at the complete translation when deciding on the evaluation of a node. The translation could have content
added before or after the node which changes its structure or meaning. If an extra component is prepended to a structural node,
for example, it should be marked as “Bad”.
